---
title: "Bank Locations Analysis"
author: "Jacob Schwan"
date: "12/12/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
pacman::p_load(tidyverse)
```


Download Institutions & Location data


```{r}
if(!file.exists("Offices2.zip")) {
    download.file("https://www5.fdic.gov/idasp/Offices2.zip",
                  "Offices2.zip")
}

unzip("Offices2.zip")
```

Looks like they provide a nice data dictionary

```{r}
read_csv("OFFICES2_DEFINITIONS.CSV") %>%
    View("Data Dictionary")
```

Looks like we actucally would be better served with the Summary of Deposits data set=

```{r}
if(!file.exists("SOD2018.zip")) {
    download.file("https://www5.fdic.gov/sod/download/ALL_2018.ZIP",
                  "ALL_2018.ZIP")
}

unzip("ALL_2018.ZIP")

#Data dictionary
if(!file.exists("sod_variables_definitions.xls")) {
    download.file("https://www5.fdic.gov/sod/pdf/sod_variables_definitions.xls",
                  "sod_variables_definitions.xls")
}
```



```{r}
sod_2018 <- read_csv("ALL_2018.csv")
```

```{r}
sod_2018_1 <- read_csv("ALL_2018_1.csv")
```

```{r}
sod_2018_2 <- read_csv("ALL_2018_2.csv")
```

```{r}
nrow(sod_2018_1) + nrow(sod_2018_2)
```

So 1 & 2 and just ALL broken up in some way...

```{r}
sod_2018 %>%
    count(STNAMEBR, sort = T)
```

```{r}
sod_2018 %>%
    distinct(STNAMEBR, NAMEFULL) %>%
    count(STNAMEBR, sort = T)
```

Minnesota is thrid highest in unique banks with 297 compared to only 160 in Nebraska

```{r}
(anb_msas <- sod_2018 %>%
    filter(CERT == "19300") %>%
    count(NAMEFULL, STNAMEBR, MSANAMB, MSABR, CERT))
```

Just banks in our MSA

```{r}
sod_2018 %>% 
    filter(MSABR %in% c(33460,36540)) %>%
    distinct(MSANAMB, NAMEFULL) %>%
    count(MSANAMB, sort = T)
```

There are over twice as many banks present in MSP as there are in OCB

```{r}
anb_primary_msas <- sod_2018 %>%
    filter(MSABR %in% c(33460,36540))
```

```{r}
anb_primary_msas %>%
    distinct(NAMEFULL, MSABR, .keep_all = T) %>%
    select(MSANAMB, NAMEFULL, ASSET) %>%
    group_by(MSANAMB) %>%
    summarise(ASSET = sum(ASSET))
```

```{r}
pacman::p_load(tidycensus)
```

